### 2012-10-13 Docs/Thesis/introduction.tex
Thesis: rewrote introduction ending

The first challenge was addressed by representing FRP programs, not as compositions of signals and events, but as compositions of
{\em transformers} of behaviors and events called {\em signal functions}. By not permitting direct access to behaviors or events, but
representing them implicitly, signal functions prohibit accessing past or future time values, only allowing access to values in the closure of the signal function
and current input values. Signal function FRP programs are written by composing signal functions, and are evaluated using a function which provides input to the
signal function and acts on the output values. This evaluation function is elided in existing literature on signal functions. 
A further advantage of signal function FRP programs is that they are more compositional, since additional signal functions may be composed
on the input or output side of a signal function, rather than simply the output side in classic (non-signal-function) FRP systems.

@@

N-ary FRP provides a model of a type system for a push-based signal-function FRP system. In order to represent signal functions
as continuations on collections of inputs rather than on single values, we represent the signal vectors as types over which
the signal function type is parameterized for both inputs and outputs. Indices into the signal vector are typed with the signal vector. These indices
contain the actual input or output values and form elements for a collection of inputs or outputs. Obviously the collection need not have all possible elements,
which forms the basis for evaluating only those parts of the network which depend on the updated values.

>>>>

The first challenge was addressed by representing FRP programs, not as compositions of signals and events, but as compositions of
transformers of behaviors and events called {\em signal functions}. By not permitting direct access to behaviors or events, but
representing them implicitly, signal functions prohibit accessing past or future time values, only allowing access to values in the closure of the signal function
and current input values. Signal function FRP programs are written by composing signal functions, and are evaluated using a function which provides input to the
signal function and acts on the output values. This evaluation function is elided in existing literature on signal functions. 
A further advantage of signal function FRP programs is that they are more compositional, since additional signal functions may be composed
on the input or output side of a signal function, rather than simply the output side in classic (non-signal-function) FRP systems.

@@

This thesis describes the design and implementation of Time-Flies, a push-pull signal-function FRP system. This system is presented as a library
of combinators for constructing and evaluating FRP programs.
